LSOA Deprevation maps

### 2021-09-06 LSOA Deprevation.Rmd
Tweaking bits

```{r Mapping the Indices of deprivation for the LSOA}
lsoa_multidep_merged_sf<- merge(lsoa_sf_data, lsoa_multidep)
ggplot2::ggplot(lsoa_multidep_merged_sf)+
  geom_sf(aes(fill=IMDScore))+
  scale_fill_continuous(name="IMD Score", low="green", high="red")+
  labs(caption="Solent (all LSOAs)")
```

#####Looking at the cities in more detail
```{r Southampton LSOA Indices of dep}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Southampton")

@@

#Histogram
lsoa_imd20152019$pc_diff <-100* (lsoa_imd20152019$imd_diff/lsoa_imd20152019$imd2015)
t_diff <-dplyr::select(as.data.frame(lsoa_imd20152019),LSOA11CD, lsoa11cd, imd2015, imd2019, imd_diff, pc_diff)
head(arrange(t_diff, pc_diff))
head(arrange(t_diff, -pc_diff))
ggplot2::ggplot(t_diff, aes(x=pc_diff)) +
  geom_histogram()
```
#####Looking at the cities in more detail
```{r Southampton LSOA IMD}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_imd20152019, LADnm == "Southampton") # check names of variables! Use the data file with the geometry in it
# plotting the gas consumption of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = imd_diff)) +
  scale_fill_continuous(name = "Change in IMD score", low = "green", high = "red") +
  labs(caption = "Southampton")
```
```{r Portsmouth LSOA IMD}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(lsoa_imd20152019, LADnm == "Portsmouth")
# plotting the gas consumption of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `imd_diff`)) +
  scale_fill_continuous(name = "Change in IMD score", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Winchester LSOA Gas}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_imd20152019, LADnm == "Winchester")
# plotting the gas consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `imd_diff`)) +
  scale_fill_continuous(name = "Change in IMD score", low = "green", high = "red") +
  labs(caption = "Winchester")
```

>>>>

```{r Mapping the Indices of deprivation for the LSOA}
lsoa_multidep_merged_sf<- merge(lsoa_sf_data, lsoa_multidep)
ggplot2::ggplot(lsoa_multidep_merged_sf)+
  geom_sf(aes(fill=IMDScore))+
  scale_fill_continuous(name="IMD Score", low="green", high="red")+
  labs(caption="Solent (all LSOAs)")
```
####Map with overlay 
```{r Check leaflet for change i dom gas consumption}
library(leaflet)

st_coord_sys <- st_crs(lsoa_multidep_merged_sf)
st_coord_sys$epsg

#Transforming the coor system
if(st_coord_sys$epsg !=4326){
  map_df_trans <- st_transform(lsoa_multidep_merged_sf, "+proj=longlat +datum=WGS84")
}

```
```{r Plotting leaflet for change in dom gas consumption map}
qpal <- colorNumeric("Reds", map_df_trans$IMDScore, n=9)

leaflet(map_df_trans) %>%
  addTiles() %>%
  addPolygons(color = ~qpal(IMDScore),
              fillOpacity = 0.6, weight = 1.5, popup = ~(LSOA11CD),

               highlight = highlightOptions(
                weight = 5,
                color = "#666",
                fillOpacity = 0.7,
                bringToFront = TRUE))

```
```{r Southampton LSOA Indices of dep}
#####Looking at the cities in more detail
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_multidep_merged_sf, LAD11NM == "Southampton")

@@

#Histogram
lsoa_imd20152019$pc_diff <-100* (lsoa_imd20152019$imd_diff/lsoa_imd20152019$imd2015)
t_diff <-dplyr::select(as.data.frame(lsoa_imd20152019),LSOA11CD, lsoa11cd, imd2015, imd2019, imd_diff, pc_diff)
head(arrange(t_diff, pc_diff))
head(arrange(t_diff, -pc_diff))
ggplot2::ggplot(t_diff, aes(x=pc_diff)) +
  geom_histogram()
```
####Map with overlay 
```{r Check leaflet for change i dom gas consumption}
library(leaflet)

st_coord_sys <- st_crs(lsoa_imd20152019)
st_coord_sys$epsg

#Transforming the coor system
if(st_coord_sys$epsg !=4326){
  map_df_trans <- st_transform(lsoa_imd20152019, "+proj=longlat +datum=WGS84")
}

```
```{r Plotting leaflet for change in dom gas consumption map}
qpal <- colorNumeric("Reds", map_df_trans$imd_diff, n=9)

leaflet(map_df_trans) %>%
  addTiles() %>%
  addPolygons(color = ~qpal(imd_diff),
              fillOpacity = 0.6, weight = 1.5, popup = ~(LSOA11CD),

               highlight = highlightOptions(
                weight = 5,
                color = "#666",
                fillOpacity = 0.7,
                bringToFront = TRUE))

```

#####Looking at the cities in more detail
```{r Southampton LSOA IMD}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_imd20152019, LADnm == "Southampton") # check names of variables! Use the data file with the geometry in it
# plotting the gas consumption of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = imd_diff)) +
  scale_fill_continuous(name = "Change in IMD score", low = "green", high = "red") +
  labs(caption = "Southampton")
#Histogram
mapData$imd_diff <-100* (mapData$imd_diff/mapData$imd2015)
t_diff <-dplyr::select(as.data.frame(lsoa_imd20152019),LSOA11CD, lsoa11cd, imd2015, imd2019, imd_diff, pc_diff)
head(arrange(t_diff, pc_diff))
head(arrange(t_diff, -pc_diff))
ggplot2::ggplot(t_diff, aes(x=pc_diff)) +
  geom_histogram()
```
```{r Portsmouth LSOA IMD}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(lsoa_imd20152019, LADnm == "Portsmouth")
# plotting the gas consumption of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `imd_diff`)) +
  scale_fill_continuous(name = "Change in IMD score", low = "green", high = "red") +
  labs(caption = "Portsmouth")
#Histogram
mapData$imd_diff <-100* (mapData$imd_diff/mapData$imd2015)
t_diff <-dplyr::select(as.data.frame(lsoa_imd20152019),LSOA11CD, lsoa11cd, imd2015, imd2019, imd_diff, pc_diff)
head(arrange(t_diff, pc_diff))
head(arrange(t_diff, -pc_diff))
ggplot2::ggplot(t_diff, aes(x=pc_diff)) +
  geom_histogram()
```
```{r Winchester LSOA Gas}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_imd20152019, LADnm == "Winchester")
# plotting the gas consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `imd_diff`)) +
  scale_fill_continuous(name = "Change in IMD score", low = "green", high = "red") +
  labs(caption = "Winchester")
#Histogram
mapData$imd_diff <-100* (mapData$imd_diff/mapData$imd2015)
t_diff <-dplyr::select(as.data.frame(lsoa_imd20152019),LSOA11CD, lsoa11cd, imd2015, imd2019, imd_diff, pc_diff)
head(arrange(t_diff, pc_diff))
head(arrange(t_diff, -pc_diff))
ggplot2::ggplot(t_diff, aes(x=pc_diff)) +
  geom_histogram()
```
####Plotting the relationship between deprevation and Fuel Poverty
